Replication

### 2024-02-13 output/paper/paper.qmd
format of paper

---
title: "Replication"
author: Yingzhi Zhang
date: today
date-format: long
abstract: 
format: pdf
header-includes: 
- \usepackage{float}
mainfont: Times New Roman
sansfont: Times New Roman
number-sections: true
bibliography: references.bib
toc: true
---

@@

```{r}
#| echo: false
#| eval: false
#| warning: false
#| message: false
#| include: false
#| label: tbl-01
#| tbl-cap: "First ten rows of the cleaned crisis call data"
#| tbl-cap-location: bottom
#| tbl-pos: H

@@

```{r}
#| echo: false
#| eval: false
#| warning: false
#| message: false
#| include:false
#| label: fig-type
#| fig-cap: "Trend of crisis calls by type over time"
#| fig-pos: H
#| fig-width: 7
#| fig-height: 3

@@

```{r}
#| echo: false
#| eval: false
#| warning: false
#| message: false
#| include:false
#| label: fig-time
#| fig-cap: "Distribution of crisis calls over the day by type"
#| fig-pos: H
#| fig-width: 7
#| fig-height: 3

@@

```{r}
#| echo: false
#| eval: false
#| warning: false
#| message: false
#| include: false
#| label: fig-location
#| fig-cap: "Number of crisis calls in different neighbourhoods classified by types"
#| fig-width: 8
#| fig-height: 9
#| fig-pos: H

>>>>

---
title: "Replication"
author: Yingzhi Zhang
date: today
date-format: long
abstract: "the abstract of the paper"
format: pdf
header-includes: 
- \usepackage{float}
mainfont: Times New Roman
sansfont: Times New Roman
number-sections: true
toc: true
---

@@

```{r}
#| echo: false
#| eval: false
#| warning: false
#| message: false
#| label: tbl-01
#| tbl-cap: "First ten rows of the cleaned crisis call data"
#| tbl-cap-location: bottom
#| tbl-pos: H

@@

```{r}
#| echo: false
#| eval: false
#| warning: false
#| message: false
#| label: fig-type
#| fig-cap: "Trend of crisis calls by type over time"
#| fig-pos: H
#| fig-width: 7
#| fig-height: 3

@@

```{r}
#| echo: false
#| eval: false
#| warning: false
#| message: false
#| label: fig-time
#| fig-cap: "Distribution of crisis calls over the day by type"
#| fig-pos: H
#| fig-width: 7
#| fig-height: 3

@@

```{r}
#| echo: false
#| eval: false
#| warning: false
#| message: false
#| label: fig-location
#| fig-cap: "Number of crisis calls in different neighbourhoods classified by types"
#| fig-width: 8
#| fig-height: 9
#| fig-pos: H
